---
title: "Journal 1"
#bibliography: Collins, R., & Steffen-Fluhr, N. (2019). Hidden patterns: Using social network analysis to track career trajectories of women STEM faculty. Equality, Diversity and Inclusion: An International Journal.bib
author: "Electra"
#research q:
"Does female researchers’ social network, in the Science department, include more male academics when the faculty board is gender balanced rather than male-dominated?"

---
r

There is a gender gap in STEM studies due to traditional gender roles, stereotypes and gender inequality. As a result fewer women decide to follow these studies and it is much harder for them according to literature() to advance. In this research we focus on these women's social network. it seems that when is male dominated male tend to collaborate with men. will be something diffrent if it's gender neutral? 
as a sample I will use the faculty of scinece of Utrecth uni and Radboud the former is gender neutral and the other male dominated. I will take at least one female worker from each uni and compare. 


reference

Collins, R., & Steffen-Fluhr, N. (2019). Hidden patterns: Using social network analysis to track career trajectories of women STEM faculty. Equality, Diversity and Inclusion: An International Journal.

Casad, B. J., Franks, J. E., Garasky, C. E., Kittleman, M. M., Roesler, A. C., Hall, D. Y., & Petzel, Z. W. (2021). Gender inequality in academia: Problems and solutions for women faculty in STEM. Journal of neuroscience research, 99(1), 13-23.


https://www.ru.nl/science/about-the-faculty/organisation/faculty-board/
https://www.uu.nl/en/organisation/faculty-of-science/about-us/management


```{r}
"?references.bib"
```
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()



colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

Last compiled on `r format(Sys.time(), '%B, %Y')`

<br>

----
  
This is just an example page of your `r colorize("lab journal", "red")`.
You can journal the assignments of the first day here.
  

----


```{r}
print("Hello Lab Journal")
```



